---
title: "Pokemon data analysis"
output: 
    html_notebook: 
      fig_heigt: 4.5
      fig_width: 8
      number_sections: yes
      theme: flatly
      toc: yes
      toc_float: yes
---

# Abstract

https://www.youtube.com/watch?v=ZA28sOmq7nU

Pokemon data analysis workout.

# Workout

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(openxlsx)
```

## Read data 

```{r}
pokemon <- read.xlsx("Pokemon.xlsx")
```

```{r}
dim(pokemon)
```

## t test

Show plot with Type.I and Atk data.

```{r}
pokemon %>% ggplot(aes(x = Type.I, y = Atk)) + 
    geom_boxplot() + coord_flip()
```

Are means of Psychic and Rock different?

```{r}
psychic <- pokemon %>% filter(Type.I == "Psychic") %>% select(Atk)
rock <- pokemon %>% filter(Type.I == "Rock") %>% select(Atk)

t.test(psychic, rock, var.equal = FALSE)
```

Maybe they are different.

## linear regression

```{r}
pokemon %>% ggplot(aes(x = Atk, y = Def)) + 
    geom_point(aes(color = Type.I)) + stat_smooth(method = "lm", se = FALSE) + theme(legend.position = "bottom")
```

Basically Def ~ Atk ?

```{r}
regModel <- lm(Def ~ Atk, data = pokemon)

summary(regModel)
```

Plot residuals of regression model. If this regression model is really good, residuals must be distributed like normal distribution.

```{r}
tibble(x = regModel$residuals) %>% ggplot(aes(x=x)) + geom_histogram(bins = 30)
```

It is not look like normal distribution.

Taking log10(y) makes it normal?

```{r}
pokemon %>% ggplot(aes(x = Atk, y = Def)) + 
    geom_point(aes(color = Type.I)) + stat_smooth(method = "lm", se = FALSE) + 
    theme(legend.position = "bottom") + scale_y_log10()
```

```{r}
regModelLog <- lm(log10(Def) ~ Atk, data = pokemon)
```

```{r}
tibble(x = regModelLog$residuals) %>% ggplot(aes(x=x)) + geom_histogram(bins = 30)
```

Wow! It look like normal distribution, but shariro-wilk test does not return larger p-value.

```{r}
shapiro.test(regModelLog$residuals)
```

So, it is not normal anyway.

```{r}
tibble(x = regModelLog$residuals) %>% ggplot(aes(sample = x)) + geom_qq() + geom_qq_line()
```

